### 2020-05-29 README.Rmd
[docs] Fix figure path in README
[docs] Tweak figure output width
[docs] Complete repo renaming

<!-- badges: start -->
[![R build status](https://github.com/ideas-lab-nus/epluspar-paper/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/epluspar-paper/actions)
<!-- badges: end -->

@@

```{r, echo = FALSE}
knitr::include_graphics(here::here("figures/artifact.png"))
```

@@

You can download the compendium as a zip from from this URL:
<https://github.com/ideas-lab-nus/epluspar-paper/archive/master.zip>

Or you can install this compendium as an R package, epluspar-paper, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ideas-lab-nus/epluspar-paper")
```

>>>>

<!-- badges: start -->
[![R build status](https://github.com/ideas-lab-nus/eplusr-paper/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/eplusr-paper/actions)
<!-- badges: end -->

@@

```{r, echo = FALSE, out.width = "30%"}
knitr::include_graphics("figures/artifact.png")
```

@@

You can download the compendium as a zip from from this URL:
<https://github.com/ideas-lab-nus/eplusr-paper/archive/master.zip>

Or you can install this compendium as an R package, eplusr-paper, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ideas-lab-nus/eplusr-paper")
```
